---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-figures/",
  out.width = "100%"
)

devtools::load_all()

library(wesandersoncast)
wes_actors <- wesandersoncast::wes_actors
```

# wesandersoncast

<!-- badges: start -->

[![R-CMD-check](https://github.com/KellyTall/wesandersoncast/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/KellyTall/wesandersoncast/actions/workflows/R-CMD-check.yaml) [![License: CC0](https://img.shields.io/badge/License-CC0%201.0-lightgrey.svg)](https://creativecommons.org/publicdomain/zero/1.0/)
![Last update](https://img.shields.io/badge/updated-May_2025-blue)
![Built with Wikidata](https://img.shields.io/badge/Built%20with-Wikidata-informational?logo=wikidata&logoColor=white&color=brightgreen)

<!-- badges: end -->

**wesandersoncast** (v0.1.0.9001) is a lightweight R package that provides a tidy dataset of actors appearing in films directed by **Wes Anderson**. It includes each film's title, release year, runtime, and worldwide box office takings — all sourced from [Wikidata](https://www.wikidata.org/wiki/Wikidata:Main_Page).

The dataset is ideal for demonstrations, tutorials, and exploration of network relationships or filmography trends using the tidyverse.

## 📦 Dataset contents

The `wes_actors` dataset is a tibble with `r nrow(wes_actors)` rows and `r ncol(wes_actors)` variables:

| Column | Type | Description |
|-----------------|-----------------|---------------------------------------|
| `film` | character | Title of the film directed by Wes Anderson |
| `actor` | character | Name of the actor appearing in the film |
| `release_date` | date | First screening date of the film |
| `box_office_usd` | numeric | Worldwide box office gross (in USD, where available) |
| `duration_period` | lubridate Period | Duration of the film in hours and minutes (e.g. "1H 45M") |

## 📝 Data Notes

-   *Castello Cavalcanti*, *Cousin Ben Troop Screening with Jason Schwartzman*, *Hotel Chevalier*, and the short film versions of *Bottle Rocket* are not included.
-   *The Wonderful Story of Henry Sugar*, *The Rat Catcher*, *Poison* and *The Swan* have no box office results as they were produced by Netflix.
-   *The Phoenician Scheme* was released in May 2025. At the time of publishing to CRAN, no box office figures were available. This will be updated once the data is released.

If you find any errors in the data, I encourage you to correct them on Wikidata — it’s an incredible community-driven resource.

## 📜 License

The dataset included in this package is dedicated to the public domain under [CC0 1.0](https://creativecommons.org/publicdomain/zero/1.0/).

(❤️ creative commons ❤️)

## 📥 Installation

You can install the development version of **wesandersoncast** from GitHub with:

``` r
# install.packages("remotes") # if not already installed
remotes::install_github("KellyTall/wesandersoncast")
```


## 🔍 Example

```{r example-usage, eval = TRUE, echo = TRUE}
library(wesandersoncast)
head(wes_actors)

```
## 📦 Version

- Current version: **0.1.0.9001**
- Last updated: **31 May 2025**

## 📅 Data Updates

- Last updated: 31 May 2025
- Total records: `r nrow(wes_actors)`
- Source: [Wikidata](%5Bhttps://www.wikidata.org)(<https://www.wikidata.org>)

## ✨ What's new in this version

Included voice actors (P725) in addition to screen actors which means *Isle of Dogs* and *Fantastic Mr Fox* now appear.
